### 2023-12-18 documentation/thesis/thesis_document.tex
more thesis

\hypertarget{user-interface}{%
\subsection{User-Interface}\label{user-interface}}

@@

@@

\begin{itemize}
\tightlist
\item
  einfache bedienung durch nutzer auch ohne weitere software
\item
  configuration
\item
  debugging
\end{itemize}

@@

Each pipeline step is divided into \passthrough{\lstinline!stages!},
which contain a name, the function to be executed and its parameters.
The various steps are then linked by using the
\passthrough{\lstinline!stage <name>!} as the input parameter of the
next function to be executed (see comments in
\ref{lst:mrpuddp_example_yaml}). It is therefore also possible to use
the results of one function in several others without them directly
following each other. The disadvantages of this system are as the
following:

\begin{itemize}
\tightlist
\item
  No loops can be created
\item
  Complex determination of the execution sequence of the steps
\end{itemize}

@@

After several simplification steps, determination of possible start
steps and repeated traversal, the final execution sequence can be
determined in the form of a call
tree\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.

@@

The individual steps are then executed along the graph. The intermediate
results and the final result are saved for later use.

\begin{itemize}
\tightlist
\item
  vorteile erleutern kurz
\end{itemize}

@@

\begin{lstlisting}[language=Python, caption={Example pytest class for testing MRPReading module functions}, label=lst:pytest_example_code]
# $ cat test_mrpreading.py
class TestMPRReading(unittest.TestCase):
  # PREPARE A INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
  def setUp(self) -> None:
      self.test_folder: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
      self.test_file:str = os.path.join(self.import_export_test_folderpath, "tmp")

  def test_matrix(self):
      reading: MRPReading = MRPSimulation.generate_reading()
      matrix: np.ndarray = reading.to_numpy_matrix()
      n_phi: float = reading.measurement_config.n_phi
      n_theta: float = reading.measurement_config.n_theta
      # CHECK MATRIX SHAPE
      self.assertTrue(matrix.shape != (n_theta,))
      self.assertTrue(len(matrix.shape) <= n_phi))

  def test_export_reading(self) -> None:
      reading: MRPReading = self.test_reading_init()
      self.assertIsNotNone(reading)
      # EXPORT READING TO A FILE
      reading.dump_to_file(self.test_file)

  def test_import_reading(self):
      # CREATE EMPTY READING
      reading_imported:MRPReading = MRPReading.MRPReading(None)
      # LOAD READING FROM FILE
      reading_imported.load_from_file(self.test_file)
      # CHECK IF ENTRIES ARE POPULATED
      self.assertIsNotNone(reading_imported.additional_data)
      self.assertIsNotNone(reading_imported.data)
\end{lstlisting}

>>>>

\hypertarget{communication-interface}{%
\subsection{Communication interface}\label{communication-interface}}

@@

Each sensor that has been loaded with the firmware, registeres on to the
host \gls{pc} as a serial interface. There are several ways for the user
to interact with this:

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp}-library (see \ref{software-readout-framework})
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows you to quickly determine
whether the hardware is working properly after installation. The
\gls{cli} behaves like terminal programmes, displaying a detailed
command reference\ref{Sensors_(+cli).png} to the user after connecting.
The current measured value can be output using the
\passthrough{\lstinline!readout!}
command\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}-library. The serial interface
is also used here. However, after a connection attempt by the
\passthrough{\lstinline!MRPHal!} module\ref{hal} of the
\gls{mrp}-library, the system switches to binary mode, which is
initiated using the \passthrough{\lstinline!sbm!} command. However, the
same commands are available as for \gls{cli}-based communication.

@@

Each pipeline step is divided into \passthrough{\lstinline!stages!},
which contain a name, the function to be executed and its parameters.
The various steps are then linked by using the
\passthrough{\lstinline!stage <name>!} as the input parameter of the
next function to be executed (see comments in
\ref{lst:mrpuddp_example_yaml}). It is therefore also possible to use
the results of one function in several others without them directly
following each other. The disadvantages of this system are the
following:

\begin{itemize}
\tightlist
\item
  No circular parameter dependencies
\item
  Complex determination of the execution sequence of the steps
\end{itemize}

@@

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
\caption{pipeline output files after running example pipeline on a set
of readings
\label{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
\end{figure}

After several simplification steps, determination of possible start
steps and repeated traversal, the final execution sequence can be
determined in the form of a call
tree\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.
The individual steps are then executed along the graph. The intermediate
results and the final
results\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
are saved for optional later use.

@@

\begin{lstlisting}[language=Python, caption={Example pytest class for testing MRPReading module functions}, label=lst:pytest_example_code]
class TestMPRReading(unittest.TestCase):
  # PREPARE A INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
  def setUp(self) -> None:
      self.test_folder: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
      self.test_file:str = os.path.join(self.import_export_test_folderpath, "tmp")

  def test_matrix(self):
      reading: MRPReading = MRPSimulation.generate_reading()
      matrix: np.ndarray = reading.to_numpy_matrix()
      n_phi: float = reading.measurement_config.n_phi
      n_theta: float = reading.measurement_config.n_theta
      # CHECK MATRIX SHAPE
      self.assertTrue(matrix.shape != (n_theta,))
      self.assertTrue(len(matrix.shape) <= n_phi)

  def test_export_reading(self) -> None:
      reading: MRPReading = MRPSimulation.generate_reading()
      self.assertIsNotNone(reading)
      # EXPORT READING TO A FILE
      reading.dump_to_file(self.test_file)

  def test_import_reading(self):
      # CREATE EMPTY READING AND LOAD FROM FILE
      reading_imported:MRPReading = MRPReading.MRPReading(None)
      reading_imported.load_from_file(self.test_file)
      # COMPARE
      self.assertIsNotNone(reading_imported.compare(MRPSimulation.generate_reading()))
\end{lstlisting}
